Human Factors Influencing Visual Statistical Inference

### 2013-06-10 sociology_paper.tex
experiment setup updated

\subsection{Individual Performance of the Observer} Each person is different from others in some way. For example, in a controlled experimental study \citet{zhao:2012}  notice that some people spend a lot of time to decide no matter whether the lineup is difficult or easy while some simply glance at lineups to make a decision. This influences the response of the observer. Also subject specific variation in the power of visual test is observed in \citep{majumder:2013}.

\section{Experimental Designs and Methods}\label{sec:exp_design}
The performance of the observer while evaluating a lineup would depend on the factors described in Section \ref{sec:factor_performance}. This section presents the simulation experimental setup, data collection methods and data analysis plans with models to asses the influence of those factors on visual statistical inference.

>>>>

\subsection{Individual Performance of the Observer} Each person is different from others in some way. For example, in a controlled experimental study \citet{zhao:2012}  noticed that some people spent a lot of time to decide no matter whether the lineup is difficult or easy while some simply glanced at lineups to make a decision. This influences the response of the observer. Also subject specific variation in the power of visual test is observed in \citep{majumder:2013}.

\section{Experimental Designs and Methods}\label{sec:exp_design}
The performance of the observer while evaluating a lineup would depend on the factors described in Section \ref{sec:factor_performance}. Some of these factors such as signal in the data and individual performances are studied in \cite{majumder:2013}. In this paper we intend to study effect of the factors such as human demographics, learning trend, actual plot locations and selection of null plots. This section presents the simulation experimental setup, data collection methods and data analysis plans with models to asses the influence of those factors on visual statistical inference.
